---
title: "Schertz City Council Documents — Prototype 3"
format:
  html: default
  typst: default
---

## What this prototype does

Prototype 3 follows the stronger pattern used in the original Framingham app:

1. discover documents
2. save prepared intermediate files
3. download PDFs
4. extract PDF text
5. build a final local search index
6. let the Shiny app read only the finished local files

The app should **not** scrape websites at startup.

## File structure

- `app.R` — thin Shiny app that reads `data/derived/documents.rds`
- `R/00_config.R` — config and shared helpers
- `R/discover_city_hub.R` — reads the Schertz hub page
- `R/discover_destinyhosted.R` — discovers current City Council packet/minutes links
- `R/discover_laserfiche.R` — archive scaffold
- `R/normalize_documents.R` — unifies source outputs
- `R/download_documents.R` — downloads PDFs to `data/raw/`
- `R/extract_text.R` — extracts full text with `pdftools`
- `R/build_search_data.R` — builds final `documents.rds` and `documents.csv`
- `R/run_pipeline.R` — orchestrates the pipeline

## Recommended first run

```{r}

source("R/run_pipeline.R")

docs <- schertz_build_index(
  download_files = TRUE,
  extract_text = TRUE,
  include_archive = FALSE,
  start_year = 2019L
)

```

Then launch the app:

```{r}

shiny::runApp("app.R", launch.browser = TRUE)

```

## What to expect

The app becomes meaningfully searchable only after:
- PDFs have been downloaded
- text has been extracted
- `data/derived/documents.rds` has been rebuilt

Useful checks:

```{r}

nrow(docs)
sum(nzchar(docs$text_extracted), na.rm = TRUE)
table(docs$doc_type, useNA = "ifany")
head(docs[, c("meeting_date", "title", "doc_type", "text_available")], 20)

```

## Intermediate files

This prototype deliberately saves intermediate outputs in `data/derived/`, including:

- `city_hub_links.rds`
- `destinyhosted_raw_links.rds`
- `destinyhosted_documents.rds`
- `documents_normalized.rds`
- `documents_downloaded.rds`
- `documents_with_text.rds`
- final `documents.rds`

That makes debugging easier and keeps the app lightweight.

## Important limitation

The Laserfiche archive stage is still conservative. Prototype 3 is mainly aimed at making the **current-system text extraction pipeline** solid before deeper archive crawling.

### Diagnostic Code

```{r}
table(docs$text_available, useNA = "ifany")
```


```{r}
docs |>
  dplyr::filter(grepl("budget", search_text, ignore.case = TRUE)) |>
  dplyr::select(meeting_date, title, doc_type) |>
  head(20)
```


### Testing New Module for Collecting Minutes Data

Test 1

```{r}
source("R/00_config.R")
source("R/discover_laserfiche_minutes.R")

lf_minutes <- schertz_discover_laserfiche_minutes()

dplyr::glimpse(lf_minutes)

```

Test 2

```{r}
root_page <- schertz_laserfiche_minutes_links(
  "https://laserfiche.schertzweb.com/WebLink/Browse.aspx?id=545783&dbid=1&repo=SCHERTZ",
  cfg = schertz_config
)

root_page |>
  dplyr::select(link_text, absolute_url, is_browse, is_docview) |>
  print(n = 100)

```

Test 3

```{r}
page <- xml2::read_html("https://laserfiche.schertzweb.com/WebLink/Browse.aspx?id=545783&dbid=1&repo=SCHERTZ")

rvest::html_elements(page, "a") |>
  rvest::html_attr("href") |>
  head(50)

```

Test 4

```{r}
page |>
  rvest::html_elements("title, body, script, iframe, frame") |>
  rvest::html_text2() |>
  print()

```

Test 5

```{r}
cat(as.character(page), sep = "\n")

```

Test 6

```{r}
js <- readLines(
  "https://laserfiche.schertzweb.com/WebLink/bundles/app.bundle.js?v=10.2",
  warn = FALSE
)

stringr::str_extract_all(
  paste(js, collapse = " "),
  "api/[A-Za-z0-9_./?=&-]+|Browse\\.aspx\\?[A-Za-z0-9_./?=&-]+|DocView\\.aspx\\?[A-Za-z0-9_./?=&-]+"
) |>
  unlist() |>
  unique() |>
  sort() |>
  print()

```

Test 7

```{r}
txt <- paste(js, collapse = " ")

patterns <- c(
  "rootFolder", "folderId", "entryId", "children", "document",
  "browse", "export", "search", "repo", "dbid"
)

hits <- unlist(lapply(patterns, function(pat) {
  m <- gregexpr(pat, txt, ignore.case = TRUE)[[1]]
  if (m[1] == -1) return(character(0))
  starts <- pmax(1, m - 120)
  ends <- pmin(nchar(txt), m + 220)
  vapply(seq_along(starts), function(i) substr(txt, starts[i], ends[i]), character(1))
}))

unique(hits) |>
  head(50) |>
  print()
```

Test 8

```{r}
resp <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetFolderListing") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(list(repoName = "SCHERTZ", folderId = 545783), auto_unbox = TRUE) |>
  httr2::req_perform()

txt <- httr2::resp_body_string(resp)
cat(txt)

```

Test 9

```{r}
resp2 <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetFolderListing2") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(
    list(
      repoName = "SCHERTZ",
      folderId = 545783,
      getNewListing = TRUE,
      start = 0,
      end = 200,
      sortColumn = "",
      sortAscending = TRUE
    ),
    auto_unbox = TRUE
  ) |>
  httr2::req_perform()

cat(httr2::resp_body_string(resp2))

```

Test 10

```{r}
lf_json <- jsonlite::fromJSON(httr2::resp_body_string(resp2), simplifyDataFrame = TRUE)

tibble::as_tibble(lf_json$data$results) |>
  dplyr::select(name, entryId, type, extension, isEdoc) |>
  print(n = 50)
```

Test 11

```{r}
lf_2025_2026 <- tibble::as_tibble(lf_json$data$results) |>
  dplyr::filter(!is.na(entryId), isEdoc, extension == "pdf") |>
  dplyr::mutate(
    document_url = paste0(
      "https://laserfiche.schertzweb.com/WebLink/DocView.aspx?id=",
      entryId,
      "&dbid=1&repo=SCHERTZ"
    )
  ) |>
  dplyr::select(name, entryId, document_url)

lf_2025_2026 |>
  print(n = 50)
```

Test 12

```{r}
resp3 <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetBreadCrumbs") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(
    list(
      vdirName = "WebLink",
      repoName = "SCHERTZ",
      folderId = 545783
    ),
    auto_unbox = TRUE
  ) |>
  httr2::req_perform()

bc <- jsonlite::fromJSON(httr2::resp_body_string(resp3), simplifyDataFrame = TRUE)

print(bc)
```

Test 13

```{r}
resp4 <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetFolderListing2") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(
    list(
      repoName = "SCHERTZ",
      folderId = 54085,
      getNewListing = TRUE,
      start = 0,
      end = 200,
      sortColumn = "",
      sortAscending = TRUE
    ),
    auto_unbox = TRUE
  ) |>
  httr2::req_perform()

fy_json <- jsonlite::fromJSON(httr2::resp_body_string(resp4), simplifyDataFrame = TRUE)

tibble::as_tibble(fy_json$data$results) |>
  dplyr::select(name, entryId, type, extension, isEdoc) |>
  print(n = 100)
```

Test 14

```{r}
fy_json$data$totalEntries
```

Test 15

```{r}
resp5 <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetFolderListing2") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(
    list(
      repoName = "SCHERTZ",
      folderId = 54085,
      getNewListing = TRUE,
      start = 0,
      end = 100,
      sortColumn = "",
      sortAscending = TRUE
    ),
    auto_unbox = TRUE
  ) |>
  httr2::req_perform()

fy_json2 <- jsonlite::fromJSON(httr2::resp_body_string(resp5), simplifyDataFrame = TRUE)

tibble::as_tibble(fy_json2$data$results) |>
  dplyr::filter(!is.na(entryId)) |>
  dplyr::select(name, entryId, type, extension, isEdoc) |>
  print(n = 100)

```

Test 16

```{r}
resp6 <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetFolderListing2") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(
    list(
      repoName = "SCHERTZ",
      folderId = 54085,
      getNewListing = TRUE,
      start = 40,
      end = 80,
      sortColumn = "",
      sortAscending = TRUE
    ),
    auto_unbox = TRUE
  ) |>
  httr2::req_perform()

fy_json3 <- jsonlite::fromJSON(httr2::resp_body_string(resp6), simplifyDataFrame = TRUE)

tibble::as_tibble(fy_json3$data$results) |>
  dplyr::filter(!is.na(entryId)) |>
  dplyr::select(name, entryId, type, extension, isEdoc) |>
  print(n = 100)

```

Test 17

```{r}
tibble::as_tibble(fy_json2$data$results) |>
  dplyr::slice_tail(n = 10) |>
  dplyr::select(name, entryId)
```

Test 18

```{r}
resp7 <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetFolderListingIds") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(
    list(
      repoName = "SCHERTZ",
      folderId = 54085,
      sortColumn = "",
      sortAscending = TRUE
    ),
    auto_unbox = TRUE
  ) |>
  httr2::req_perform()

cat(httr2::resp_body_string(resp7))
```

Test 19

```{r}
all_ids <- jsonlite::fromJSON(httr2::resp_body_string(resp7), simplifyVector = TRUE)$data

visible_ids <- tibble::as_tibble(fy_json2$data$results) |>
  dplyr::filter(!is.na(entryId)) |>
  dplyr::pull(entryId) |>
  as.character()

setdiff(all_ids, visible_ids)
```

Test 20

```{r}
purrr::map_dfr(
  setdiff(all_ids, visible_ids)[1:10],
  function(id) {
    resp_tmp <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetBreadCrumbs") |>
      httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
      httr2::req_body_json(
        list(
          vdirName = "WebLink",
          repoName = "SCHERTZ",
          folderId = as.integer(id)
        ),
        auto_unbox = TRUE
      ) |>
      httr2::req_perform()

    bc_tmp <- jsonlite::fromJSON(httr2::resp_body_string(resp_tmp), simplifyDataFrame = TRUE)

    tibble::tibble(
      entryId = id,
      last_name = tail(bc_tmp$data$name, 1)
    )
  }
)

```

Test 21

```{r}
resp8 <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetFolderListing2") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(
    list(
      repoName = "SCHERTZ",
      folderId = 48605,
      getNewListing = TRUE,
      start = 0,
      end = 200,
      sortColumn = "",
      sortAscending = TRUE
    ),
    auto_unbox = TRUE
  ) |>
  httr2::req_perform()

cat(httr2::resp_body_string(resp8))
```

Test 22

```{r}
fy_1998_1999 <- jsonlite::fromJSON(httr2::resp_body_string(resp8), simplifyDataFrame = TRUE)

tibble::as_tibble(fy_1998_1999$data$results) |>
  dplyr::select(name, entryId, type, extension, isEdoc) |>
  print(n = 100)
```

Test 23

```{r}
resp9 <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetDocumentInfo") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(
    list(
      repoName = "SCHERTZ",
      dId = 41673
    ),
    auto_unbox = TRUE
  ) |>
  httr2::req_perform()

cat(httr2::resp_body_string(resp9))

```

Test 24

```{r}
jsonlite::fromJSON(httr2::resp_body_string(resp9), simplifyDataFrame = FALSE)

```

Test 25

```{r}
doc_page <- xml2::read_html("https://laserfiche.schertzweb.com/WebLink/DocView.aspx?id=41673&dbid=1&repo=SCHERTZ")

doc_page |>
  rvest::html_elements("title, body") |>
  rvest::html_text2() |>
  print()

```

Test 26

```{r}
resp10 <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetDocumentInfo") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(
    list(
      repoName = "SCHERTZ",
      dId = 546331
    ),
    auto_unbox = TRUE
  ) |>
  httr2::req_perform()

jsonlite::fromJSON(httr2::resp_body_string(resp10), simplifyDataFrame = FALSE)
```

Test 27

```{r}
test_ids <- c(546331, 547235, 545989, 41673, 41688)

purrr::map_dfr(
  test_ids,
  function(id) {
    resp_tmp <- httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetDocumentInfo") |>
      httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
      httr2::req_body_json(
        list(
          repoName = "SCHERTZ",
          dId = id
        ),
        auto_unbox = TRUE
      ) |>
      httr2::req_perform()

    info <- jsonlite::fromJSON(httr2::resp_body_string(resp_tmp), simplifyDataFrame = FALSE)

    tibble::tibble(
      entryId = id,
      pageCount = info$data$pageCount,
      isEdoc = info$data$isEdoc
    )
  }
)
```

Test 28

```{r}
source("R/00_config.R")
source("R/discover_laserfiche_minutes.R")

lf_minutes <- schertz_discover_laserfiche_minutes()

dplyr::glimpse(lf_minutes)
```

Test 29

```{r}
schertz_laserfiche_service_post <- function(endpoint, body, max_tries = 5L) {
  url <- paste0(
    "https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/",
    endpoint
  )

  last_err <- NULL

  for (i in seq_len(max_tries)) {
    out <- tryCatch(
      {
        httr2::request(url) |>
          httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
          httr2::req_body_json(body, auto_unbox = TRUE) |>
          httr2::req_perform() |>
          httr2::resp_body_string()
      },
      error = function(e) {
        last_err <<- e
        NULL
      }
    )

    if (!is.null(out)) {
      return(out)
    }

    message(
      "Laserfiche retry ", i, "/", max_tries,
      " for ", endpoint, " failed: ",
      conditionMessage(last_err)
    )
    Sys.sleep(1.5 * i)
  }

  stop(last_err)
}

lf_minutes <- schertz_discover_laserfiche_minutes()

```

Test 29

```{r}
httr2::request("https://laserfiche.schertzweb.com/WebLink/FolderListingService.aspx/GetFolderListing2") |>
  httr2::req_headers(`Content-Type` = "application/json; charset=UTF-8") |>
  httr2::req_body_json(
    list(
      repoName = "SCHERTZ",
      folderId = 54085,
      getNewListing = TRUE,
      start = 0,
      end = 50,
      sortColumn = "",
      sortAscending = TRUE
    ),
    auto_unbox = TRUE
  ) |>
  httr2::req_perform() |>
  httr2::resp_body_string() |>
  cat()
```

Test 30

```{r}
docs <- readRDS("data/derived/documents.rds")

lf_minutes |>
  dplyr::mutate(meeting_date = as.Date(meeting_date, origin = "1970-01-01")) |>
  dplyr::inner_join(
    docs |>
      dplyr::filter(doc_type == "minutes") |>
      dplyr::select(meeting_date, title),
    by = "meeting_date",
    suffix = c("_lf", "_existing")
  ) |>
  dplyr::select(
    meeting_date,
    title_lf,
    title_existing
  ) |>
  print(n = 50)
```

Test 31

```{r}
lf_minutes |>
  dplyr::mutate(meeting_date = as.Date(meeting_date, origin = "1970-01-01")) |>
  dplyr::anti_join(
    docs |>
      dplyr::filter(doc_type == "minutes") |>
      dplyr::select(meeting_date),
    by = "meeting_date"
  ) |>
  dplyr::select(meeting_date, title) |>
  print(n = 50)
```

Test 32

```{r}
docs_merged <- dplyr::bind_rows(
  docs,
  lf_minutes |>
    dplyr::mutate(meeting_date = as.Date(meeting_date, origin = "1970-01-01")) |>
    dplyr::anti_join(
      docs |>
        dplyr::filter(doc_type == "minutes") |>
        dplyr::select(meeting_date),
      by = "meeting_date"
    )
)
```

Test 32

```{r}
docs_merged |>
  dplyr::count(doc_type) |>
  print()
```

Test 33

```{r}
source("R/build_search_data.R")
docs_merged <- schertz_build_search_data(docs_merged, cfg = schertz_config)
```


Test 34

```{r}
docs_merged |>
  dplyr::filter(grepl("Ralph Gutierrez", search_text, ignore.case = TRUE)) |>
  dplyr::select(meeting_date, title, doc_type, text_available, source_system) |>
  print(n = 20)
```

